\section{C++ work (fabcoind)}
\subsection{coinBaseMaturity, EvalScript}
\begin{frame}[fragile]
\frametitle{Changes to fabcoin (C++): coinBaseMaturity, EvalScript}
\begin{itemize}
\item Introduced \verb|Params::coinBaseMaturity|.
\begin{itemize}
\item If positive, overrides \verb|COINBASE_MATURITY|, ignored otherwise. 
\item Set to positive only for \verb|regtest| and \verb|testNetNoDNS|.
\item \verb|COINBASE_MATURITY|: min coin depth after which coin can be spent.
\end{itemize}
\item \verb|EvalScript|: opt. arg.: \verb|std::stringstream* extraErrorStream|
\begin{itemize}
	\item If zero: ignored. No performance penalty.
	\item Default: zero. No need to refactor.
	\item If non-zero, provides additional debug messages.
	\item Non-zero only for \verb|regtest| and \verb|testNetNoDNS|, governed by \verb|Params::fAllowExtraErrorStream|.
\end{itemize}
\end{itemize}

\end{frame}

\subsection{New RPC calls}
\begin{frame}[fragile]
\frametitle{Changes to fabcoin (C++): new RPC calls}
\begin{itemize}
\item Introduced: \verb|sendbulkrawtransactions|. 
\begin{itemize}
\item Like \verb|sendrawtransaction| but with comma-separated transactions.
\item Rationale: can send $1000$ transactions with a single HTTP post.
\end{itemize}
\item Introduced: \verb|getperformanceprofile|.
\begin{itemize}
\item Returns a performance profile. 
\item Already detailed, to be made far more so.
\end{itemize}
\end{itemize}

\end{frame}
\subsection{getperformanceprofile}
\begin{frame}[fragile]
\frametitle{getperformance profile implementation}
\begin{itemize}
\item RAII performance profiler.
\begin{verbatim}
void first(...) {
    FunctionProfile profileThis("functionToProfile");
    //useful work }
void second(...) {
    FunctionProfile profileThis("functionToProfile");
    //useful work
    first(); }
\end{verbatim}
\item Distinguishes between different call stacks. 
\item In above: statistics collected for: \verb|first|, \verb|second|, \verb|second->first| (first called from inside second). Sample output:
\begin{tabular}{|r|r|r|r|}\hline
f-n& \# calls & run time& run time excl. subordinates \\\hline
\verb|first| & 10& 10 ms & 10 ms\\\hline
\verb|second| & 5& 20 ms& 15 ms\\\hline
\verb|second->first|& 5& 5 ms & 5 ms\\\hline
\end{tabular}
\item To be greatly expanded.
\end{itemize}
\end{frame}

\section{Node.js work}
\begin{frame}[fragile]
\frametitle{Node.js work}
\begin{itemize}
\item Implemented \verb|POST| calls on RPC ports
\begin{itemize}
\item All nets: \verb|regtest|, \verb|testnetnodns|, \verb|testnet|, \verb|mainnet|). 
\item Rationale: \verb|child.spawn| breaks large inputs $600$kb with fabcoin-cli.
\end{itemize}
\item Towards profiling: generated $1$ large transaction and $1000$ small transactions.
\[
25 \stackrel{tx_0}{\mapsto} \left\{\begin{array}{lll}
0.025 & \stackrel{tx_1}{\mapsto}& 0.0245 \\
0.025 & \stackrel{tx_1}{\mapsto}& 0.0245\\
\vdots\\
0.025 & \stackrel{tx_1}{\mapsto}& 0.0245
\end{array} \right.
\]
\item Numerous changes in user interface.
\item To do: make transaction go through (violates fabcoin protections).
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{To do}
\begin{itemize}
\item Finish profiling of large transactions.
\end{itemize}
\end{frame}