\section{C++}
\subsection{Flags and options}
\begin{frame}[fragile]
\frametitle{Changes to fabcoin (C++)}
\begin{itemize}
\item Introduced \verb|CChainParams::fDebugInfoRegtestAndTestNetNoDNSOnly|.
\begin{itemize}
\item \verb|regtest|, \verb|testNetNoDNS| only.
\item Gives more detailed explanations on RPC errors.
\end{itemize}
\item Introduced  \verb|nDefaultDescendantLimit|
\begin{itemize}
	\item If positive, overrides \verb|DEFAULT_DESCENDANT_LIMIT|
	\item Overridden in turn by command line argument 
	
\end{itemize}
\item Introduced \verb|nDefaultDescendantSizeLimit|: similar to  \verb|nDefaultDescendantLimit|.

\item Introduced \verb|Profiling::fAllowProfiling|, new fabcoind options: \verb|-profilingon|, \verb|profilingoff|. 
\begin{itemize}
	\item If false, no profiling code is executed (immediate return all f-n calls).
	\item Turned off by \verb|-profilingoff|, turned on by \verb|-profilingoff|.
	\item If neither \verb|-profilingoff|, \verb|-profilingoff| given, turned on for \verb|regtest|, \verb|testNetNoDNS|,
	off for \verb|mainNet|, \verb|testNet|.
\end{itemize}

\end{itemize}

\end{frame}

\subsection{Profiling}

\begin{frame}[fragile]
\frametitle{Profiling: run-time histograms}
\begin{itemize}
\item Generating run-time histograms profiled function calls. 
\item Histogram buckets labeled by function execution times.
\item Each histogram bucket contains the number of function calls with the given execution time.
\item Example: bucket labeled $(5,15] \mu s$ contains all function calls that had a run-time between $5$ and $15$ $\mu s$.
\item Histograms have \verb|Statistic::desiredNumberOfHistogramBucketsMinusOne = 100| buckets.
\item The bucket sizes are chosen after an initial sample of runs.
\item No histograms before initial sample run.
\item secp256k1 signatures are hardened against timing attacks $\Rightarrow$ no obvious security risks when profiling.
\item However, profiling considered insecure until deeper thought has been given.
\end{itemize}
\end{frame}
\begin{frame}[fragile]
\frametitle{Profiling: txid arrival times}
\begin{itemize}
\item Turned on/off via \verb|Profiling::fAllowTxIdReceiveTimeLogging|.
\item Alternatively, turned on/off via  \verb|-profilingoff|, \verb|-profilingon|.
\item Off by default for \verb|mainNet|, \verb|testNet|.
\item Recording statistics with arrival times (in ms) of the most recent \verb|Profiling::nMaxNumberTxsToAccount=20000| transactions.
\item No obvious security risk, however considered insecure until deeper thought has been given.
\end{itemize}
\end{frame}


\subsection{New RPC calls}
\begin{frame}[fragile]
\frametitle{New RPC calls}
\begin{itemize}
\item New RPC call: \verb|getperformanceprofile|
\begin{itemize}
	\item Turned off when profiling is off.
	
\end{itemize}
\item New RPC call: \verb|getmemorypoolarrivaltimes|
\begin{itemize}
	\item Turned off when profiling is off.
\end{itemize}
\end{itemize}
\end{frame}

\section{Node.js}
\begin{frame}
\frametitle{Work on node.js server}
\begin{itemize}
\item Histograms visualized via chart.js.
\item User interface for new functionality.
\end{itemize}
\end{frame}
