\section{Node.js}
\begin{frame}[fragile]
\frametitle{Node.js summary}
\begin{itemize}
\item Node.js progress.
\begin{itemize}
\item Automated Jacks' smart contract deployment.
\item Automated KanbanGO deployment on regtest.
\item Work on a smart-contract middleware mechanism: goal: smart contract calls made through human-readable api. Work in progress.
\item Deployed demo system on London \& Mumbai AWS machine.
\end{itemize}
\item Node.js: to do.
\begin{itemize}
\item Automate KanbanGO deployment on \verb|regtestwithnetwork|.
\end{itemize}
\end{itemize}
\end{frame}

\section{Fabcoind}
\begin{frame}[fragile]
\frametitle{Fabcoind summary}
\begin{itemize}
\item Fabcoind progress.
\begin{itemize}
\item Aggregate signature fully supported via a new opcode \verb|OP_AGGREGATEVERIFY|.
\item Created restricted regtest-with-network [test before testnet].
\item Deployed regtest-with network on London and Mumbai AWS.
\item Implement.: \url{https://github.com/tmilev/fabcoin-dev}
\end{itemize}
\item Fabcoind: to do.
\begin{itemize}
\item Design \& code: kanbanGO write mechanism, foundation chain.
\end{itemize} 
\end{itemize}
\end{frame}

\section{KanbanGo}
\begin{frame}[fragile]
\frametitle{KanbanGo summary}
\begin{itemize}
\item KanbanGo: progress.
\begin{itemize}
\item Implemented: general-purpose voting (consensus) machine for asynchronous message signing. \item Voting machine: used to write on foundation chain.
\end{itemize}
\item KanbanGO: to do.
\begin{itemize}
\item Hook up voting machine to write mechanism on found. chain.
\item Hook up voting machine \& secure to Kanban Chain.
\end{itemize}
\end{itemize}

\end{frame}


\begin{frame}[fragile]
\frametitle{Fabcoind progress}
\begin{itemize}
\item Fabcoind progress:
\begin{itemize}
\item Opcode: \verb|OP_AGGREGATEVERIFY| works fully. Can send from any unlock script to and from an aggregate signature.
\end{itemize}
\item Fabcoind to do:
\begin{itemize}
\item Design and implement write mechanism from kanbanGO to foundation chain.
\end{itemize}
\end{itemize}
\end{frame}

