\begin{frame}[fragile]
\frametitle{Unlock for shardAggregateAddress: update}
\begin{itemize}
\item $\fcCancel{2}{\text{Previous version: shard authority via:}}$

$\fcCancel{2}{\text{contract} \stackrel{0}{\to}\text{shardAggregateAddress} }$

\item \alertNoH{3}{Found simpler approach.}
\begin{enumerate}
\item<4-> Use solidity logs, for example:
\begin{enumerate}
\item \verb|log0("KanbanAggregateSignatureUnlock")|
\item \verb|log0(pubKey1)|

\dots 

\item \verb|log0(pubKey16)|
\end{enumerate}
\item<4-> Logs: intercepted at \verb|FascState::execute|, fascstate.cpp.
\item<4-> When logs triggered as above: generate tx with unlock script:

\verb| pubkey1 ... pubkey16 OP_AGGREGATEVERIFY|
\item<4-> \verb|OP_AGGREGATEVERIFY| - newly defined opcode. 
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{OP\_AGGREGATEVERIFY}
\begin{itemize}
\item On branch: \verb|tmilev/fabcoin-dev/aggregate-signature|.
\item Forked from: \verb|blockchaingate/fabvoin-dev/sm01|.
\item So far implemented:
\begin{enumerate}
\item Opcode registration.
\item \verb|CScript::IsPayToAggregateSignature|
\item Schnorr and aggregate signature crypto library. 
\item Crypto code taken from Kanban proof of concept \verb|tmilev/kanban-poc|.
\item Code based on secp256k1 library. All non-secp256k1 functionality implemented in-house.

\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{OP\_AGGREGATEVERIFY: to do}
\begin{itemize}
\item Bootstrap crypto test RPC calls (regtest only):
\begin{verbatim}
if (chainparams.NetworkIDString() == "regtest") {
    RegisterTestCommands(tableRPC);
}
\end{verbatim}

To do: make RegisterTestCommands work properly.
\item C++ crypto library is several iterations behind its GO counterpart: update.
\item Ensure C++ crypto matches GO crypto 100\% (pubKey sort, serialization, prefixes, encodings, defaults, \dots).
\item Attach crypto library to \verb|OP_AGGREGATEVERIFY| evaluation in \verb|bool EvalScript(..)|.
\end{itemize}
\end{frame}