\begin{frame}
\begin{itemize}
\item Node.js. 
\begin{itemize}
\item Work done.
\begin{itemize}
\item Fixed memory leak in server.
\item Fixed bug: fabcoind logs were not showing correctly.
\item Added monitoring infrastructure to help prevent a future leak.
\item Log files.
\item Reworked transaction builder user inteface: fabcoind and kanbanGO.
\end{itemize}
\item To do.
\begin{itemize}
\item Create an ssh tunnel user interface.
\end{itemize}
\end{itemize}
\item KanbanGO: work done.
\begin{itemize}
\item Fixed a flexible transaction format for SCAR write operations. New coinbase-like transaction \& new opcode.
\item Transaction builder now signs the input transactions.
\item KanbabGO $SHA256^{\circ 2}$ ECDSA implementation. 
\item KanbanGO: one private key now supports Schnorr, ECDSA $SHA256^{\circ 2}$ and ECDSA keccak signatures.
\item RPC calls for testing the above.
\end{itemize}
\item KanbanGO: to do.
\begin{itemize}
\item Ensure transaction built in KanbanGO passes through fabcoind.
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Fabcoind}
\begin{itemize}
\item Work done.
\begin{itemize}
\item New function \verb|CScript::FitsOpCodePattern|.
\item Added human-readable reports to the internals of the system.
\item Bug fixes in debug-session logs. 
\item New opcode : \verb|OP_CONTRACTCOVERSFEES|.
\item New transaction type \verb|contract_covers_fees|. 
\item New coinbase-like transaction txid.
\end{itemize}
\item To do.
\begin{itemize}
\item Insert code to accept \verb|OP_CONTRACTCOVERSFEES|. 
\item Insert code to accept the new coinbase-like transaction txid.
\item Both of these require modifications of:
\begin{itemize}
\item Memory pool acceptance code.
\item Block verification code.
\item ... and possibly more?
\end{itemize}
\end{itemize}
\end{itemize}

\end{frame}