\begin{frame}
\frametitle{KanbanGO smart contract data structures}
\begin{itemize}
\item Nodes: an iterable map of nodes: 

\hfil\hfil
$\text{Nodes}:\text{bytes32}\to \text{Node}$
\item Accounts: an iterable map of accounts:

\hfil\hfil$\text{Accounts}: address \to \text{uint256}$
\item Shards: an iterable map of shards:

\hfil\hfil$\text{Shards}: bytes32 \to \text{Shard}$
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{KanbanGO smart contract first interface}

\begin{itemize}
\item \verb|RegisterNode(publicKey PubKey, [...])| returns bool.
\item \verb|SenderHasAuthorizedAggregateSignature(bytes32 ShardId)| returns bool.
\item \verb|SenderIsHandledBy(bytes32 ShardId)| returns bool.
\item \verb|ReFormAllShards()| private, public when developing.
\item \verb|GetShardPubkeys(bytes32 shardId)| returns bytes33.
\item \verb|GetMyShard(address myAccountAddress)| returns bytes32.
\item \verb|ModifyAccounts(...)| returns bool.
\end{itemize}
\end{frame}


\begin{frame}[fragile]
\frametitle{Workflow for KanbanGO bootstrap}

\begin{itemize}
\item Create blank contract.
\item \begin{enumerate}
\item KB1 executes \verb|RegisterNode|. Besides data, KB1 inputs deposit.

...

\item KB16 executes \verb|RegisterNode|.  Besides data, KB16 inputs deposit.
\end{enumerate}
\item Call \verb|ReFormAllShards|. This will do the following.
\begin{enumerate}
\item Sort the public keys and compute $ \text{shardAggregateAddres} = SHA3(\text{pubKey1},\dots, \text{pubKey16})$
\item $\text{contract} \stackrel{0}{\to}\text{shardAggregateAddress} $
\item The transformation above is going to have a special unlock script.
\end{enumerate}
\item Start the KB shard.
\begin{enumerate}
\item Periodically, KB machines agree on inputs to \verb|ModifyAccounts| via a fault-tolerant aggregate signature. 
\item The fault tolerant signature is used as inputs to the unlock script to perform \verb|ModifyAccounts(...)|.
\item In the same transaction as the contract call to  \verb|ModifyAccounts(...)|, we generate the vout for the next \verb|ModifyAccounts(...)| call.

\item Repeat.
\end{enumerate}
\end{itemize}

\end{frame}

\begin{frame}[fragile]
\frametitle{Security: unlock script for shardAggregateAddress}
\begin{itemize}
\item When bootstrapping the kb nodes, an transaction is generated:

$\text{contract} \stackrel{0}{\to}\text{shardAggregateAddress} $

\item Unlock script of above = critically important security lock.
\item Unlock script format:

$\text{shardAggregateAddress} ~\text{OP\_AGGREGATE\_SIGNATURE\_VERIFY} $

\item To unlock:
\begin{itemize}
\item Push on the stack the public keys KB1, \dots, KB16.
\item Push on the stack the aggregate fault-tolerant signature of KB1, \dots, KB16.
\item The fabcoind function $\text{VerifyScript}$ will be extended to execute a cryptographic call whenever it sees $OP\_AGGREGATE\_SIGNATURE\_VERIFY$.
\item The opcode shall flush the entire stack into the cpp function.
\item The cpp function will verify that the pubkeys match the aggregate address and that the pubkeys match the aggregate signature for the message.
\end{itemize}
\end{itemize}
\end{frame}