\section{Current architecture plan}
\begin{frame}
\frametitle{Current architecture}
\begin{itemize}
\item OS: Ubuntu at the moment. Aspirations to support everything.
\item<2-> Computational engine in openCL/C/C++.
\begin{itemize}
\item<3-> Crypto functions in openCL/C++.
\item<4-> Data management? Expected solution: stl library (no database).
\end{itemize}
\item<5-> Networking, management, testing, other non-computational tasks: nodejs.
\end{itemize}
\end{frame}
\section{Computational engine}
\subsection{Cryptography}
\begin{frame}[fragile]
\frametitle{Computational engine: cryptography}
Core crypto functions: code compiled as both openCL/C++.
\begin{itemize}
\item<2-> Forked Pieter Wuille's secp256k1 library (used in fabcoin \& bitcoin).
\item<3-> Heavy but formal modifications.
\begin{itemize}
\item<4-> openCL major memory types: \verb|__local|, \verb|__global|, \verb|__constant|
\item<5-> Mixed arguments: 1 version per combination:
\medskip


{
\tiny
\verb|secp256k1_fe_mul_inner(uint32_t *r, const uint32_t *a, __global const uint32_t * b) |

\verb|secp256k1_fe_mul_inner(uint32_t *r, const uint32_t *a, __local const uint32_t * b) |

\verb|secp256k1_fe_mul_inner(uint32_t *r, const uint32_t *a, __constant const uint32_t * b) |
}

\medskip
\item<6-> No C++ templates in openCL: emulate with macros.
\item<7-> No \verb|free|, \verb|malloc|: custom memory pools: 0 runtime memory allocation, minimal openCL-statically allocated RAM memory use
\end{itemize}
\item<8-> 4 basic modes of running. TO DO: combine (arbitrarily?).
\begin{enumerate}
\item openCL on GPU.
\item openCL on CPU.
\item C/C++ on CPU using openCL entry points.
\item C/C++ direct function call.
\end{enumerate}
\item<9-> TO DO: computation load balancing.

\end{itemize}
\end{frame}

\begin{frame}[fragile]
Core crypto: errors.
\begin{itemize}
\item No debugger.
\item Error hunting: hardcore: not even \verb|printf| available!
\item At least 4 types of errors seen so far:
\begin{itemize}
\item Easy: compiles as C/C++, doesn't as openCL or other way round.
\item Easy: runtime errors show in C/C++. 
\begin{itemize}
\item Fix: use \verb|printf|, temporarily breaking openCL, debug as usual.
\end{itemize}
\item Harder: C/C++ runs correctly, openCL crashes.
\begin{itemize}
\item Manually return from offending function.
\item Print memory pool \& compare with C/C++ output. 
\end{itemize}
\item Hard core: 1 machine/setup works correctly, another doesn't.
\begin{itemize}
\item Fix?
\end{itemize}
\end{itemize}
\end{itemize}
Core crypto: testing.
\begin{itemize}
\item Compare 4 modes of running against one another.
\item Generate signatures \& verify. 
\item Tamper signature and invalidate.
\item Compare outputs with same input between runs.
\end{itemize}


\end{frame}

\subsection{C++ driver}
\begin{frame}[fragile]
\frametitle{Computational engine: C++ driver}
\begin{itemize}
\item 3 Binary pipes: 
\begin{itemize}
\item Command pipe 
\begin{itemize}
\item nodejs $\longrightarrow$ C++. 
\item nodejs end: non-blocking; C++ end: blocking.
\end{itemize} 
\item Input data pipe
\begin{itemize}
\item nodejs $\longrightarrow$ C++.
\item nodejs end: non-blocking; C++ end: blocking.
\end{itemize} 
\item Data pipe nodejs $\leftarrow$ C++. 
\begin{itemize}
\item nodejs $\longleftarrow$ C++.
\item nodejs end: non-blocking; C++ end: blocking.
\end{itemize}
\end{itemize}
\item TCP protocol: chosen over named/unnamed pipe, std::cin/std::cout (portability).
\item Nodejs $\leftrightarrow$ C++ communication local: no networking, no authentication, no encoding.
\end{itemize}

\end{frame}

\section{nodejs}
\begin{frame}[fragile]
\frametitle{Nodejs: networking and management}
\begin{itemize}
\item TO DO: Networking.
\begin{itemize}
\item p2p discovery (FAB RPC call, Nader's smart engine, ...)
\item Kanban id: which peers are running Kanban? Quick options:
\begin{enumerate}
\item Use FAB rpc: \verb|getPeerInfo|, get IP addresses; connect on separate port to ask whether they run Kanban.
\item Alternatively, add Kanban discovery information to \verb|getPeerInfo|.
\item Alternatively, make new RPC function, e.g., \verb|getKanbanPeerInfo|.
\item Alternatively, proposals? Do Kanban p2p in a brand new way or as part of FAB RPC calls?
\end{enumerate}
\end{itemize} 
\item Data.
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{To do list for next week(s)}
Immediate to do list.
\begin{enumerate}
\item Figure out crypto bug(s) causing inconsistent runs across machines (work machines works correctly, laptop doesn't). 
\item At the moment, tests are parallelized, node runtime is not. Fix. 
\item Add timing tests for 
\begin{itemize}
\item Signature on the CPU.
\item Signature verification on the CPU and GPU.
\item Public key generation on the CPU and GPU.
\end{itemize}
\item Bootstrap a powerful machine for all tests.
\end{enumerate}

To do list for the near future.

\begin{enumerate}
\item Start signing and verifying actual transactions.
\item Implement in-RAM data search.
\item p2p network discovery.
\item Write heavy test suites.
\item Prepare detailed benchmarks.
\end{enumerate}
\end{frame}